### 2021-07-03 docs/manuscript/manuscript.tex
Add link to source code
Add expression dynamics

@@

Hierarchical clustering of spatiotemporal expression profiles showed that GRNs
with topologies that seemed to be very different have indeed very similar
expression dynamics. We expected to find GRNs with the same topology to group
together but instead we found GRNs with different topologies grouped as close
neighbors (Fig~\ref{fig:clustering}A). More interestingly, some GRNs displaying
very abundant network topologies were grouped together with GRNs displaying
very infrequent network topologies.

@@

>>>>

The source code for the genetic algorithm and other parts of analysis is available at
\url{https://github.com/Nesper94/gene-regulatory-networks}.

@@

Hierarchical clustering of spatiotemporal expression profiles showed that GRNs
with topologies that seemed to be very different have indeed very similar
expression dynamics. We expected to find GRNs with the same topology to group
together but instead we found GRNs with different topologies grouped as close
neighbors (Fig~\ref{fig:clustering}A). More interestingly, some GRNs displaying
very abundant network topologies were grouped together with GRNs displaying
very infrequent network topologies, indicating that additional interactions
in the networks have often the function of fine tunning gene expression, instead
of drastically changing the expression mechanism. This can be seen in the
expression dynamics of networks with different topologies (\nameref{S7_Fig}).

@@

\paragraph*{S7 Fig.}
\label{S7_Fig}
{\bf Expression dynamics of main networks.}
